Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-03 main.tex
tentative new version of abstract

    \begin{abstract}
        \skug{Fullness score (how much text is available): 0-none to 5 - everything.

        Polishedness score (how well-written is the chapter): 0 messy - 5 very clean.
        }
        TODO: Insert abstract
    \end{abstract}

    \begin{IEEEkeywords}
        Scheduling, Adaptive Scheduling, DAG
    \end{IEEEkeywords}

>>>>

    \begin{abstract}

        %Scheduling scientific workflows is important. (\skug{can't imagine a good first sentence})
        Scientific workflows are often represented as directed acyclic graphs (DAGs),
        where vertices correspond to tasks and edges represent the dependencies between them.
        Typically, each task requires a
        certain amount of memory to be executed and needs to communicate data to its successor tasks.
        The goal is generally to execute the workflow  as fast as possible (i.e., to minimize its makespan), 
        while satisfying the memory constraints.  
        Hence, we investigate the memory-aware scheduling of DAG-shaped workflows onto 
        heterogeneous platforms, where each processor can have a different speed and a different memory size.
        We propose a variant of HEFT (Heterogeneous Earliest Finish Time) that accounts for memory, and 
        that includes eviction strategies for cases when it might be beneficial to remove some data from memory
	in order to have enough memory to execute other tasks.
%
	Furthermore, while HEFT assumes a perfect knowledge of the execution time and memory usage
	of each task, the actual values might differ upon execution. Thus, we propose an adaptive
	scheduling strategy, where a schedule is recomputed when there has been a significant variation in terms
	of execution time or memory. 
%	
	The scheduler has been closely integrated with a runtime system, allowing us to perform a thorough
	experimental evaluation on real-world workflows. The runtime system warns the scheduler when 
	the task parameters have changed, and a schedule can be recomputed on the fly. The memory-aware
	strategy allows us to schedule task graphs that would run out of memory with a state-of-the-art
	scheduler, and the adaptive setting allows us to significantly reduce the makespan.

%                when tentatively assigning tasks, in order to 
%        Its first step is to compute the weights of the tasks.
%        We suggest three variants: bottom levels as weights, bottom levels with impact of incoming edge weight,
%        and weights along the optimal memory traversal.
%        In the second step, we try assigning each task to each processors and execute the assignment that
%        is feasible with regard to memory size and gives the earliest finishing time to the task.
%        Sometimes, data corresponding to edge weights that is stored in the memory needs to be evicted in order to
%        assign a task to a processor.
%        We suggest two eviction strategies - largest files first and smallest files first.

%        Our experimental evaluation on real-world workflows and simulated (\skug{generated? They are generated from real-world wfs})
%        ones with real task and edge weights with up to 30,000 tasks shows that
%        respecting memory constraints only costs $11\%$ of runtime in comparison to a non memory-aware baseline.
%        Calculating task weights with the impact of memory gives a $x\%$ better makespans on a normal and $y\%$ better makespans
%        on small one.
%        Calculating task weights along the optimal memory traversal gives on average $z\%$ worse makespans, but improves
%        average memory utlization by $t\%$.

    \end{abstract}

%    \begin{IEEEkeywords}
%        DAG, Heterogeneous platform, Adaptive scheduling, Memory constraint.
%    \end{IEEEkeywords}
